Word-Level Abstractions for Sequential Design Verification using Algebraic Geometry

### 2016-12-17 dissertation/conclude.tex
dissertation: committee review version
dissertation:after defense_update 1

\chapter{Conclusions and Future Work}
\label{ch:conclude}
This dissertation first present a new approach to perform reachability
analysis of FSMs at the word-level. It is facilitated by reproducing 
the implicit state enumeration algorithm in computer algebra and algebraic
geometry domain. The image function part is mapped to variety projection on 
next state variables. This projection is implemented by computing the 
Gr\"obner basis of the elimination ideal with abstraction term orders.
Moreover, the set operations in the state space is mapped to 
the arithmetic of ideals, because algebraic geometry provides a 
way to reason about the variety (solution) without actually solving the 
system of polynomials. RATO is applied to improve the Gr\"obner bases 
computation process, and a tool is developed to implement our 
word-level FSM traversal algorithm. Experiments are performed to 
analyze the reachability for circuit benchmarks and gain success.

Next, we describe a method to execute functional verification on sequential Galois field
multipliers over $\Fkk$.  The core algorithm is based on word-level unrolling of 
a Moore machine, which borrows ideas from our word-level FSM traversal 
algorithm. As a result, bit-level transition relations are represented 
as a polynomial with word-level inputs/outputs.
We implement our algorithm with both \textsc{Singular} platform and C++ toolset 
and perform experiments on Agnew's SMPO and RH-SMPO.
Our approach is able to verify up to 162-bit sequential
circuits, whereas contemporary techniques fail beyond 23-bit
datapaths.

At last we explore abstraction refinement techniques to boost sequential circuit verification.
UNSAT core extraction, as an indispensable component of many refinement algorithms 
which rely on UNSAT informations, is thus proposed in polynomial rings.
We use weak Nullstellensatz as essential theory of UNSAT core extraction, 
then develop heuristics depending on the structural information of the refutation.
An algorithm was implemented within the \textsc{Singular} computer algebra tool
and experiments were conducted to validate the approach.

Our approaches still have limitations: for word-level FSM traversal and 
sequential GF multipliers verification, our method are more efficient
on XOR-rich circuits, while most industrial designs are AND-OR gates dominant.
For UNSAT core extractions, the abstraction refinement approach such as $k$-BMC 
has only limited application on certain model checking problems. To overcome these limitations,
further explorations are needed for my research.

\section{Future Work}
In this section, we point out some research problems that deserve further study.
\subsection{Multivariate polynomial ideal based FSM Traversal}
In Chapter \ref{ch:reacha}, we always use a single word-level variable $T$ to denote 
next state. However, in some situations we need to keep recording the relations between $T$ and
inputs, {\it i.e.} the reached states contain multivariate polynomials in $T,S$ and PI $x$. 
While the elimination and set union/intersection are compatible with multiple NS variables,
the set complement requires an extension to Theorem \ref{thm:quotient} on ideals with 
multivariate polynomial generators. We make a conjecture as follows:

\begin{Conjecture}
Assume we are given 2 ring variables $x,y$, and an ideal $J$ composed by 2 generators:
$J = \langle f_y, v_x\rangle$. Here $f_y$ has the form $f_y = \mathcal F(x,y)$, where $\mathcal F$
is a 2-argument function, e.g. $f_y = y^2+(1+x)y+x$. And $v_x$ is the vanishing polynomial for variable
$x$: $v_x = x^{q_1} - x$. Now we have another generator serving as the universal set
$J_0 = \langle v_x, v_y\rangle$, $v_y = y^{q_2} - y$.
We conjecture that
$$V_K(J_0:J) = V_K(J_0)\setminus V_K(J)$$
And we believe this conjecture is scalable such that it is also valid for even more variables and generators like 
$J = \langle f_z, v_x,v_y,v_u,v_w\rangle$, $f_z =\mathcal F (z,x,y,u,w)$.
\end{Conjecture}

@@

\subsection{Use F-4 and ZDDs to Accelerate Polynomial Reduction}
In Chapter \ref{ch:reacha} and Chapter \ref{ch:normal}, by using RATO we transform the GB 
computation to a multivariate polynomial division. However, this division (reduction)
is still with exponential complexity at worst case. In a situation where 
a chain of OR gate exists, the size of polynomial will explode. For example, a chain of OR gates 
which can be written as Boolean function 
\begin{equation}
\label{eqn:chainOR}
f = ((a\lor b) \lor c) \lor d
\end{equation}
equals to following polynomial function in $\F_2$:
$$f = abcd+abc+abd+ab+acd+ac+ad+a+bcd+bc+bd+b+cd+c+d$$
Notice $f$ contains $2^4-1 = 15$ terms, which is exponential to number of variables.
The polynomial size explosion is a major factor affect the efficiency of polynomial division.

One way to further boost the efficiency is to adopt techniques from sparse linear algebra.
Analysis on experiment results shows major time consumption is on multivariate polynomial division procedure.
A matrix-based technique named as "F-4 style reduction" \cite{f4} can speed up the procedure
dividing a low-degree polynomial with term-sparse polynomial ideal.

Another way is to utilize DDs, {\it e.g.} ZDDs. ZDDs can represent unate covers of Boolean formulas.
We can represent $f$ using a ZDD, while the dotted edges denote the corresponding literal does not 
exist in a minterm.

\begin{figure}[h]
\centerline{
\includegraphics[width=\textwidth]{newfig/red_steps}
}
\caption{The reduction process of chain of OR gates represent using ZDDs with order $d>c>b>a$}
\label{fig:ZDD}
\end{figure}

From Figure \ref{fig:ZDD} we find the size of the ZDD on the right-most side representing 
Equation \ref{eqn:chainOR} is $2\times4 -1 = 7$, which is linear to the number of variables.
The reduction process using ZDDs can be executed as in \cite{polybori:2009}. The graphical illustration 
of reduction in ZDDs is also shown in Figure \ref{fig:ZDD}.

\subsection{Interpolation extraction using GB Algorithm}
The concept of Craig Interpolants (CI) and their existence comes from
symbolic logic \cite{craig-interpolate}; later, algorithms were
presented to find the CI for Boolean formulae
\cite{pudlak:ci} \cite{mcmillan2003interpolation}. Assume that Boolean
formulae are represented in Clause Normal Form (CNF) as 
$f = C_1 \wedge C_2 \wedge \dots \wedge C_m$ where: 1) Each clause
$C_i$ is a disjunction (Boolean OR, denoted $\vee$) of literals; 2)
Each literal is a Boolean variable $x_i$ or its complement
$\overline{x_i}$. 
The Boolean satisfiability (SAT) problem requires that we find an
assignment to the variables such that the formula $f$ is satisfied
(SAT), or otherwise prove that no such assignment exists (UNSAT). 
A CI is related to an UNSAT formula.

\begin{Definition}
(From \cite{mcmillan2003interpolation}) Let $A$ and $B$ be Boolean
  formulae given as sets of clauses such that $A \wedge B$ is
  unsatisfiable (UNSAT). Then there exists a formula $P$ such that: 
1) $A$ implies $P$ (or $A \subseteq P$); ~2) $P \wedge B$ is UNSAT; ~iii)
$P$ refers to only the common variables of $A$ and $B$. The formula
$P$ represents an {\bf interpolant} of $A$ and $B$.

@@

{\bf Research problem 1:}
{\it As we wish to perform MC with abstraction using algebraic
  geometry, we introduce the algebraic geometry analog of CI
  and explore algorithms to compute them. We conjecture that the
  concept of CI should be related to elimination ideals, so our line
  of investigation will focus on \Grobner basis computations with
  elimination term orders for their computation.
}

@@

In the above definition $V_{\Fq}(J_A+J_B)=\emptyset$ implies that the
ideal $J_A+J_B$ has an empty variety (UNSAT) problem.

@@

{\bf Research problem 2:}
{\it How can this algebraic interpolant $f_p$ (or in the general case,
  the set of polynomials $F_P$) be computed? As the interpolant $F_P$ 
contains only variables $X_C$ that are common to the polynomial sets
$F_A, F_B$, does this imply that the interpolants can be computed by
means of \Grobner bases with an elimination term order $X_A>X_B>X_C$
with $X_A, X_B$ eliminated from the problem? }

We believe that algebraic interpolation is strongly related
to the GB computation with the elimination order $X_A>X_B>X_C$, and
this relationship needs to be formally derived.

@@

The aforementioned experiments in Example \ref{ex3} do not invalidate
our conjectures, therefore we will attempt to prove them. If we are
able to prove our conjectures, then we will further study the proof to
derive efficient algorithms to compute the algebraic
interpolants. Moreover, the above experiment shows that there can be
multiple ways of computing the interpolants. What can these \Grobner
basis computations tell us about the number of valid algebraic
interpolants for any given problem? Can they be classified as {\it weak
  or strong interpolants} based on the sparsity of the polynomials
(power of abstraction)?

{\bf Research problem 3:}
As there can be many interpolants for an ideal-pair $(J_A, J_B)$, we
will further resolve these questions:
\bi
\item Find the minimal interpolant: i.e. find the interpolant $F_P$
  such that $V(J_P)$ is the smallest variety larger than $V(J_A)$ such
  that $V(J_P) \cap V(J_B) = \emptyset$.
\item Analogously, find the maximal interpolant. 
\item Over finite fields, the variety of an elimination ideal is
  exactly equal to the projection of the variety on the un-eliminated
  variables. Consider Fig. \ref{fig:projection}, where variety of the
  ideals $J_A, J_B$ are respectively projected on the common variables
  $X_C = \{a, c\}$. Then, does computing $F_{P1}$ (resp. $F_{P2}$) 
  deliver the minimal (resp. maximal) interpolant?
\ei

\begin{figure}[h]
\centering{
\includegraphics[width=4.5in]{newfig/project.eps}
\caption{Algebraic interpolant: Projection of varieties on common variables? }
\label{fig:projection}}
\end{figure}

Once these problems are understood and algorithms for the computation
of algebraic interpolants derived, then we will integrate them 
with word-level reachability analysis for abstraction-based model
checking.

>>>>

\chapter{Conclusions and Future Work}
\label{ch:conclude}
This dissertation presents a new approach to perform reachability
analysis of FSMs at the word-level. It is facilitated by investigating the analog of 
implicit state enumeration algorithm in computer algebra and algebraic
geometry domains. The image function part of the computation is mapped to a variety projection on 
next state variables. This projection is implemented by computing the 
Gr\"obner basis of an elimination ideal with abstraction term orders.
Moreover, the set operations in the state space are mapped to 
the arithmetic of ideals, as algebraic geometry provides a 
way to reason about the variety (solutions) by manipulating the ideals.
A special term order (RATO) is utilized to improve the Gr\"obner bases 
computation, and a tool is developed to implement our 
word-level FSM traversal algorithm. Experiments are performed to 
analyze the reachability for ISCAS'89 and ITC'99 circuit benchmarks.

Next, we describe a method to execute functional verification on sequential Galois field
multipliers over $\Fkk$.  The core algorithm is based on word-level unrolling of 
a Moore machine, which applies concepts from the word-level FSM traversal 
algorithm. As a result, transition relations are represented 
as a polynomial with word-level inputs/outputs.
We implement our algorithm with both the \textsc{Singular} platform and a custom C++ toolset 
and perform experiments on two classes of circuits.
Our approach is able to verify up to 162-bit sequential
circuits, whereas contemporary techniques fail beyond 23-bit
datapaths.

At last we explore abstraction UNSAT cores in algebraic geometry -- the foundation for refinement techniques
to boost sequential circuit verification.
% UNSAT core extraction, as an indispensable component of many refinement algorithms 
% which rely on UNSAT informations, is thus proposed in polynomial rings.
We use the Weak Nullstellensatz as the essential theory of UNSAT core extraction, 
then develop heuristics to improve the core that exploit the structure of the refutation proof.
An algorithm was implemented within the \textsc{Singular} computer algebra tool
and experiments were conducted to validate the approach.

Our approaches still have limitations: for word-level FSM traversal and 
sequential GF multiplier verification, our methods are more efficient
for XOR-rich circuits, while most industrial designs are AND-OR gate dominant.
For UNSAT core extraction, the abstraction refinement approach such as $k$-BMC 
has only limited application on certain model checking problems. To overcome these limitations,
the following further explorations are worthy of investigation.

\section{Future Work}
In this section, we highlight some research problems that deserve further study.
\subsection{Multivariate Polynomial Ideal based FSM Traversal}
In Chapter \ref{ch:reacha}, we always use a single word-level variable $T$ to denote the
next state. However, in some situations we need to keep recording the relations between $T$ and
inputs, {\it i.e.} the reached states contain multivariate polynomials in $T,S$ and PI $x$. 
While the elimination and set union/intersection are compatible with multiple NS variables,
the set complement requires an extension of Theorem \ref{thm:quotient} on ideals with 
multivariate polynomial generators. We conjecture as follows:

\begin{Conjecture}
Assume we are given ring variables $x_i$, and an ideal $J$ composed by $s$ generators:
$J = \langle f_1,\dots, f_s\rangle$.  Additionally $J_0$ is the vanishing polynomial for variables
$x_i$: $ x_i^{q} - x_i$ where $q$ is the size of signal $x_i$ represents.
We conjecture that
$$V(J') = V(J_0:J) = V(J_0)\setminus V(J) = \overline{V(J)}$$
% And we believe this conjecture is scalable such that it is also valid for even more variables and generators like 
% $J = \langle f_z, v_x,v_y,v_u,v_w\rangle$, $f_z =\mathcal F (z,x,y,u,w)$.
\end{Conjecture}

In univariate case, $\F[x]$ is the principle ideal domain thus Theorem \ref{thm:quotient} can be proved.
However over multivariate case, the proof of this conjecture is not available.

@@

\subsection{Use of the $F_4$ Algorithm and ZDDs to Accelerate GB Reduction}
In Chapters \ref{ch:reacha} and \ref{ch:normal}, by using RATO we transform the GB-based
computation to that of a multivariate polynomial division. However, this division (reduction)
still incurs exponential complexity in the worst case. In a situation where division is to be performed modulo
a chain of OR gates, the size of remainder polynomial will explode. For example, a chain of OR gates 
can be written as the Boolean function 
\begin{equation}
\label{eqn:chainOR}
f = ((a\lor b) \lor c) \lor d
\end{equation}
which equals to the following polynomial function in $\F_2$:
$$f = abcd+abc+abd+ab+acd+ac+ad+a+bcd+bc+bd+b+cd+c+d$$
Notice, $f$ contains $2^4-1 = 15$ terms, which is exponential in the number of variables.
The size explosion is a major factor affecting the efficiency of polynomial division.

One way to further boost the efficiency is to adopt techniques from sparse linear algebra.
Analysis of experimental results shows that multivariate polynomial division procedure
consumes most of the verification time.
A matrix-based technique named as "$F_4$ style reduction" \cite{f4} can speed up the procedure of
dividing a low-degree polynomial with a term-sparse polynomial ideal.

Another way is to utilize DDs, {\it e.g.} ZDDs. ZDDs can represent unate covers of Boolean formulas.
We can represent $f$ using a ZDD, where every path in the ZDD from a root to a terminal corresponds
to a monomial term.

\begin{figure}[h]
\centerline{
\includegraphics[width=0.35\textwidth]{newfig/ZDD.eps}
}
\caption{A ZDD representing remainder polynomial reducing by a chain of OR gates with order $d>c>b>a$}
\label{fig:ZDD}
\end{figure}

Figure \ref{fig:ZDD} shows a ZDD representing 
Equation \ref{eqn:chainOR} with size $2\times4 -1 = 7$, which is linear in the number of variables.
The reduction process using ZDDs can be executed as in \cite{polybori:2009}. The graphical illustration 
of the remainder in ZDDs is also shown in Figure \ref{fig:ZDD}.

\subsection{Craig Interpolants in Algebraic Geometry}
The concept of Craig Interpolants (CI) and their existence comes from
symbolic logic \cite{craig-interpolate}; later, algorithms were
presented to find the CI for Boolean formulae
\cite{pudlak:ci} \cite{mcmillan2003interpolation}. Assume that Boolean
formulae are represented in Clause Normal Form (CNF) as 
$f = C_1 \wedge C_2 \wedge \dots \wedge C_m$ where: 1) Each clause
$C_i$ is a disjunction (Boolean OR, denoted $\vee$) of literals; 2)
Each literal is a Boolean variable $x_i$ or its complement
$\overline{x_i}$. 
The Boolean satisfiability (SAT) problem requires that we find an
assignment to the variables such that the formula $f$ is satisfied
(SAT), or otherwise prove that no such assignment exists (UNSAT). 
A CI is related to an UNSAT formula.

\begin{Definition}
(From \cite{mcmillan2003interpolation}) Let $A$ and $B$ be Boolean
  formulas given as sets of clauses such that $A \wedge B$ is
  unsatisfiable (UNSAT). Then there exists a formula $P$ such that: 
1) $A$ implies $P$ (or $A \subseteq P$); ~2) $P \wedge B$ is UNSAT; ~3)
$P$ refers to only the common variables of $A$ and $B$. The formula
$P$ represents an {\bf interpolant} of $A$ and $B$.

@@

We introduce the algebraic geometry analog of CI.
We conjecture that the
  concept of CI should be related to elimination ideals, so future lines
  of investigation should focus on \Grobner basis computations with
  elimination term orders for their computation.

@@

Existence of algebraic interpolant comes from \cite{craig-interpolate}.
The question for exploring is that how do we compute it in algebraic geometry?

@@

% {\bf Research problem 2:}
% {\it How can this algebraic interpolant $f_p$ (or in the general case,
%   the set of polynomials $F_P$) be computed? As the interpolant $F_P$ 
% contains only variables $X_C$ that are common to the polynomial sets
% $F_A, F_B$, does this imply that the interpolants can be computed by
% means of \Grobner bases with an elimination term order $X_A>X_B>X_C$
% with $X_A, X_B$ eliminated from the problem? }

Algebraic interpolation is strongly related
to the GB computation with the elimination order $X_A>X_B>X_C$, and
this relationship needs to be formally derived.

@@

The aforementioned experiments in Example \ref{ex3} do not invalidate
our conjectures. Moreover, the above experiment shows that there can be
multiple ways of computing the interpolants. What can these \Grobner
basis computations tell us about the number of valid algebraic
interpolants for any given problem? Can they be classified as {\it weak
  or strong interpolants} based on the sparsity of the polynomials
(power of abstraction)?

As there can be many interpolants for an ideal-pair $(J_A, J_B)$, 
the following questions should also be investigated in the future:
\bi
\item Find the minimal interpolant: {\it i.e.} find the interpolant $F_P$
  such that $V(J_P)$ is the smallest variety larger than $V(J_A)$ such
  that $V(J_P) \cap V(J_B) = \emptyset$.
\item Analogously, find the maximal interpolant. 
\item Over finite fields, the variety of an elimination ideal is
  exactly equal to the projection of the variety on the remaining
  variables. Consider Figure \ref{fig:projection}, where variety of the
  ideals $J_A, J_B$ are respectively projected on the common variables
  $X_C = \{a, c\}$. Then, does computing $F_{P1}$ (resp. $F_{P2}$) 
  deliver the minimal (resp. maximal) interpolant?
\ei

\begin{figure}[h]
\centering{
\includegraphics[width=4.5in]{newfig/project.eps}
\caption{Algebraic interpolant: Projection of varieties on common variables }
\label{fig:projection}}
\end{figure}

% 
% Once these problems are understood and algorithms for the computation
% of algebraic interpolants derived, then we will integrate them 
% with word-level reachability analysis for abstraction-based model
% checking.

### 2016-12-17 dissertation/slides/defense.tex
dissertation & slides: minor modifications before defense
dissertation:after defense_update 1

\end{tabular}
}
\end{table}
\ei
\hyperlink{motiv2}{\beamergotobutton{Recall SEC miter}}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[label = refine]{\large{Abstraction refinement}}
\begin{figure}[hbt]
\centering{
\includegraphics[width=4.5in]{../newfig/refine.eps}
\caption{Abstraction by reducing latches}
\label{fig:refine}}
\end{figure}
\vspace{-0.2in}
\bi
\item Remove ``irrelevant" latches, reduce state space
\item Provide an over-approximation
\item This algorithm requires \alert{UNSAT core extraction}
\ei
\hyperlink{motiv3}{\beamergotobutton{Recall $k$-BMC}}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[label = UNSAT]{\large{UNSAT problems: refutation within Buchberger's algorithm}}
\begin{Theorem}[Weak Nullstellensatz]
Let $J = \langle f_1,\dots, f_s \rangle $ be
an ideal in the ring $ \mathbb{F}[x_1, \dots, x_n]$ and $V_{\overline{\F}}(J)$ be its
variety over $\overline{\F}$. Then $V_{\overline{\F}}(J) = \emptyset \iff J =
\mathbb{F}[x_1,\dots,x_n] \iff 1 \in J$.  
\end{Theorem}
$V_{\overline{\F}}(J)=\emptyset \iff 1\in J \iff reduced~GB(J) = \{1\}$
\begin{Definition}
Assume a polynomial set $F$ is UNSAT. A subset $M \subseteq F$ is an {\bf UNSAT core} 
if $M$ is also UNSAT. Further, if $\forall f\in M$, $M\setminus\{f\}$ is SAT, then 
$M$ is called a {\bf minimal UNSAT core} of $F$.
\end{Definition}
\bi
\item Recall Buchberger's algorithm: UNSAT $\to$ terminates with $1$
\hyperlink{Buch}{\beamergotobutton{Buchberger}}
\pause
\item  Information lies in $Spoly$?
\item Poly calculus stronger than resolution!
\ei

@@

\begin{frame}{\large{Motivating Example: Refutation Tree}}
\vspace{-0.1in}
\includegraphics[width=3.5in]{./refutation_1.pdf}
\pause
\bi
\item $f_{10}=f_1-acf_2-af_2-f_3-cf_2-f_2 = f_1+acf_2+af_2+f_3+cf_2+f_2$
\item $1 = \F(f_1,f_2,f_3,f_4,f_5)\implies 1 \in \langle f_1,f_2,f_3,f_4,f_5\rangle \implies UNSAT$
\ei
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Reducing size: redundancy in refutation tree}}
\bi
\item Expand: \begin{align*}
		1 &= \F(f_1,f_2,f_3,f_4,f_5)\\
		&= cf_2+f_5+\alert{f_{11}}\\
		&=cf_2+f_5+f_3+f_4+\alert{f_{10}}\\
		&=(cf_2 + f_5) + \dots + \mathbf{1\cdot f_3} + \dots + \mathbf{1\cdot
  f_3}+ \dots + (f_1 + acf_2)
		\end{align*}
\item UNSAT core reduced to $\{f_1,f_2,f_4,f_5\}$ which is {\bf minimal}
\item \alert{GB-core algorithm}:
	\bi
	\item Execute Buchberger's algorithm
	\item Recording data including Spoly, polynomials for division and remainder
	\item Terminate Buchberger's algorithm after recording remainder ``1"
	\item Build refutation tree and get UNSAT core
	\item Analyze recorded data, remove redundant polynomials from the core
	\ei
\ei
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Syzygy example: setup}}
\bi
\item Syzygy matrix:
\ei
\includegraphics[width=4.5in]{./syzygy_1.pdf}
\pause
\llap{\includegraphics[width=4.5in]{./syzygy_2.pdf}}
\bi
\item rows: syzygies
\item $J = \langle f_1,f_2,\dots,f_9\rangle$
\item $f_{10}\in J$
\ei
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Syzygy Example: refine syzygy matrix}}
\bi
\item Considering $f_{10}=f_1-acf_2-af_2-f_3-cf_2-f_2 = f_1+acf_2+af_2+f_3+cf_2+f_2$
\ei
\includegraphics[width=4.5in]{./syzygy_3.pdf}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Syzygy example: derive interdependency}}
\includegraphics[width=4.5in]{./syzygy_4.pdf}
\bi
\item Column $f_3$ contains ``1", means:\\
$1\cdot f_3 + ac f_2 + a f_5 = 0\Leftrightarrow f_3 = acf_2+af_5$
\item Generalization of this strategy refer to the paper
\ei
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Overall Approach}}
\begin{algorithm}[H] % note [hbt] will fail in beamer
\SetAlgoNoLine
 \KwIn{A set of UNSAT polynomials $F$} 
 \KwOut{A subset $F'\subset F$ remains UNSAT}
 $G \gets F$\;
  \Repeat{$G=F'$}
  {
	$F' = G$\;
  	$G \gets $GB-core($F'$ with order $>$)\;
	Update order $>$\;
  }
  $F'\gets$syzygy\_heuristic($G$)\;
\Return{$F'$}
\caption {UNSAT core extraction based on Gr\"obner basis algorithm}
\end{algorithm}
\end{frame}

@@

>>>>

\end{tabular}
}
\end{table}
\ei
\hyperlink{motiv2}{\beamergotobutton{Recall SEC miter}}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[label = refine]{\large{Abstraction refinement}}
\begin{figure}[hbt]
\centering{
\includegraphics[width=4.5in]{../newfig/refine.eps}
\caption{Abstraction by reducing latches}
\label{fig:refine}}
\end{figure}
\vspace{-0.2in}
\bi
\item Remove ``irrelevant" latches, reduce state space
\item Provide an over-approximation
\item This algorithm requires \alert{UNSAT core extraction}
\ei
\hyperlink{motiv3}{\beamergotobutton{Recall $k$-BMC}}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[label = UNSAT]{\large{UNSAT problems: refutation within Buchberger's algorithm}}
\begin{Theorem}[Weak Nullstellensatz]
Let $J = \langle f_1,\dots, f_s \rangle $ be
an ideal in the ring $ \mathbb{F}[x_1, \dots, x_n]$ and $V_{\overline{\F}}(J)$ be its
variety over $\overline{\F}$. Then $V_{\overline{\F}}(J) = \emptyset \iff J =
\mathbb{F}[x_1,\dots,x_n] \iff 1 \in J$.  
\end{Theorem}
$V_{\overline{\F}}(J)=\emptyset \iff 1\in J \iff reduced~GB(J) = \{1\}$
\begin{Definition}
Assume a polynomial set $F$ is UNSAT. A subset $M \subseteq F$ is an {\bf UNSAT core} 
if $M$ is also UNSAT. Further, if $\forall f\in M$, $M\setminus\{f\}$ is SAT, then 
$M$ is called a {\bf minimal UNSAT core} of $F$.
\end{Definition}
\bi
\item Recall Buchberger's algorithm: UNSAT $\to$ terminates with $1$
\hyperlink{Buch}{\beamergotobutton{GB}}
\pause
\item  Information lies in $Spoly$?
\item Poly calculus stronger than resolution!
\ei

@@

\begin{frame}{\large{Motivating Example: Refutation Tree}}
\vspace{-0.1in}
\includegraphics[width=3.5in]{./refutation_1.pdf}
\pause
\bi
\item $f_{10}=f_1-acf_2-af_2-f_3-cf_2-f_2 = f_1+acf_2+af_2+f_3+cf_2+f_2$
\item $1 = \Func(f_1,f_2,f_3,f_4,f_5)\implies 1 \in \langle f_1,f_2,f_3,f_4,f_5\rangle \implies UNSAT$
\ei
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Reducing size: redundancy in refutation tree}}
\bi
\item Expand: \begin{align*}
		1 &= \Func(f_1,f_2,f_3,f_4,f_5)\\
		&= cf_2+f_5+\alert{f_{11}}\\
		&=cf_2+f_5+f_3+f_4+\alert{f_{10}}\\
		&=(cf_2 + f_5) + \dots + \mathbf{1\cdot f_3} + \dots + \mathbf{1\cdot
  f_3}+ \dots + (f_1 + acf_2)
		\end{align*}
\item UNSAT core reduced to $\{f_1,f_2,f_4,f_5\}$ which is {\bf minimal}
\item \alert{GB-core algorithm}:
	\bi
	\item Execute Buchberger's algorithm
	\item Recording data including Spoly, polynomials for division and remainder
	\item Terminate Buchberger's algorithm after recording remainder ``1"
	\item Build refutation tree and get UNSAT core
	\item Analyze recorded data, remove redundant polynomials from the core
	\ei
\ei
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Syzygy example: setup}}
\bi
\item Syzygy matrix:
\ei
\includegraphics[width=4.5in]{./syzygy_1.pdf}
\pause
\llap{\includegraphics[width=4.5in]{./syzygy_2.pdf}}
\bi
\item rows: syzygies
\item $J = \langle f_1,f_2,\dots,f_9\rangle$
\item $f_{10}\in J$
\ei
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Syzygy Example: refine syzygy matrix}}
\bi
\item Considering $f_{10}=f_1-acf_2-af_2-f_3-cf_2-f_2 = f_1+acf_2+af_2+f_3+cf_2+f_2$
\ei
\includegraphics[width=4.5in]{./syzygy_3.pdf}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Syzygy example: derive interdependency}}
\includegraphics[width=4.5in]{./syzygy_4.pdf}
\bi
\item Column $f_3$ contains ``1", means:\\
$1\cdot f_3 + ac f_2 + a f_5 = 0\Leftrightarrow f_3 = acf_2+af_5$
\item Generalization of this strategy refer to Ch.7 in dissertation
\ei
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{\large{Overall Approach}}
\begin{algorithm}[H] % note [hbt] will fail in beamer
\SetAlgoNoLine
 \KwIn{A set of UNSAT polynomials $F$} 
 \KwOut{A subset $F'\subset F$ remains UNSAT}
 $G \gets F$\;
  \Repeat{$G=F'$}
  {
	$F' = G$\;
  	$G \gets $GB-core($F'$ with order $>$)\;
	Update order $>$\;
  }
  $F'\gets$syzygy\_heuristic($G$)\;
\Return{$F'$}
\caption {UNSAT core extraction based on Gr\"obner basis algorithm}
\end{algorithm}
\end{frame}

@@

\begin{frame}{\large{Auf Wiedersehen}}
\includegraphics[scale=0.5]{thankyou.pdf}
